Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-13 intro.tex
started intro pass

High performance object detectors usually generalizes very well. It can handle various intraclass variability, viewpoint change and occlusion. However due to this high generalization, sometimes it is very difficult to get accurate pose, category or 2D-3D matching. Our method, specialized in giving such accurate information, can be applied on any generic object detectors to give high quality metadata.

Matching 3D CAD model to an image has been a classical problem that dates back to eighties \cite{Lowe87}. Lowe \etal , the vision community instead focused on the object detection tasks that estimates a rectangular bounding box around an object\cite{Felzenszwalb10, Girshick14}. To infer what is more than a rectangle, several attempts have been made to estimate the pose of an object \cite{Xiang12, Pepik12, Fidler12, Hejrati14} or even finding corresponding CAD model as well \cite{Aubry14, Lim14}.

However, there has been increasing demand for accurate pose and 2D-3D matching. Notably, in graphics community, there has been growing demand for accurate 2D-3D matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation, editing and data augmentation respectively.

Recently, with the powerful computing capabilities and a large collection of CAD models, the 2D-3D matching (registration) problem gets more and more approachable but due to inherent difficulty and limited performance of existing methods, many applications still require supervision to achieve 2D-3D matching.

% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.

>>>>

Current approaches to object class detection have reached a remarkable
level of performance in 2D bounding box
localization~\cite{pascal12,Felzenszwalb10,Girshick14}, due to their
ability to generalize across differences in object appearance,
lighting, and viewpoint. While this generalization
ability of these methods is benefitial for robustness, it also limits
the level of detail that these detectors can deliver as an output.

As a consequence, there has been increased interest in multi-view object
recognition, where viewpoint estimates are provided by
detectors in addition to 2D bounding boxes. Several attempts have been
made to estimate viewpoint along with object class detections,
implemented as extensions to existing detectors, such as the implicit
shape models~\cite{}, the constellation model~\cite{}, or the
deformable part model~\cite{Xiang12,Pepik12,Fidler12,Hejrati14}.

Recently, an even higher level of geometric detail was reached in the
form of aligning
3D CAD models to real world test images~\cite{Aubry14,
  Lim14}. Interestingly, the problem of matching 3D models to 2D
images has been targeted since the early days of computer
vision~\cite{Lowe87}, but had largely been neglected in recent years
in favor of 2D detectors based on robust local features and
statistical learning techniques. Now, this problem is being revisited
mostly due to two reasons: the availability of sufficient artificial
3D training data and the availability of robust image matching
techniques.
%
% performance object detectors usually generalizes very well. It
% can handle various intraclass variability, viewpoint change and
% occlusion. However due to this high generalization, sometimes it is
% very difficult to get accurate pose, category or 2D-3D matching. Our
% method, specialized in giving such accurate information, can be
% applied on any generic object detectors to give high quality metadata.
% %
% Matching 3D CAD model to an image has been a classical problem that
% dates back to eighties . Lowe \etal , the vision
% community instead focused on the object detection tasks that estimates
% a rectangular bounding box around an object\cite{Felzenszwalb10,
%   Girshick14}. 
%
In addition, there has been a growing emand for accurate 2D-3D
matching \cite{Kholgade14, Chen13, Kostas14} for image manipulation,
editing, and data augmentation in the computer graphics community.
% Recently, with the powerful computing capabilities and a large
% collection of CAD models, the 2D-3D matching (registration) problem
% gets more and more approachable but due to inherent difficulty and
% limited performance of existing methods, many applications still
% require supervision to achieve 2D-3D matching.
% In medical community, registering 3D scan data to 2D image enabled various minimally invasive surgeries \cite{Markelj12}.
